\documentclass{Class}
\input{Preamble}
\title{Assignment 2}
\author{Markus Hohwü Larsen - 202205800}
\begin{document}
\problem{1}
Let $\left(B_t\right)_{t \geq 0}$ denote a standard Brownian motion.
\begin{enumerate}
    \item Determine the distribution of $B_s+B_t$ for $0 \leq s \leq t$. Determine the distribution of $B_2^2$ and of $B_1^2+\left(B_2-B_1\right)^2$.
    \item Argue that $\mathbb{P}\left(0<B_1<B_2<B_\pi\right)=\frac{1}{8}$. Determine $\mathbb{E}\left[B_1 B_2 B_\pi \mid \mathcal{F}_2^B\right]$ and $\mathbb{E}\left[B_1 B_2 B_\pi\right]$.
    \item Define $U_t=t B_{\frac{1}{t}}$ for $t>0$. Let $0<s<t$. Determine the distribution of $U_{\text {, }}$ and of $U_t-U_s$, and determine whether $U_n$ and $U_t-U_s$ are independent.
    \\For $a \in \mathbb{R}$ let $$
    T_a=\inf \left\{t \geq 0: B_t=a\right\}
    $$Later in the course we show both that $\mathbb{P}\left(T_a<\infty\right)=1$ for all $a \in \mathbb{R}$ and that $\mathrm{P}\left(T_a<T_b\right)=b /(b-a)$ for $a<0<b$.
    \item Determine $\mathbb{P}\left(T_1<T_{-1}<T_2\right)$.
    \item Define $\left(X_t\right)_{t \geq 0}$ as $X_t=\sqrt{t} B_1$ for $t \geq 0$. Does $X_t \stackrel{t}{=} B_t$ hold for $t \geq 0$ ? Is $\left(X_t\right)_{t \geq 0}$ a Brownian motion?
    \item  Let $Y \sim N(0,1)$ and assume that $Y$ is independent of $\left(B_t\right)_{t \geq 0}$. Let

    $$
    Z_t=B_t+t\left(Y-B_1\right), \quad t \in[0,1] .
    $$
    
    
    Are $\left(B_t\right)_{t \in[0,1]}$ and $\left(Z_t\right)_{t \in[0,1]}$ versions? Are they modifications or indistinguishable (dansk: uskelnelige)?
\end{enumerate}
\solution
\begin{enumerate}
    \item 
\end{enumerate}
\problem{2}
Let $\left(N_t\right)_{t \geq 0}$ denote a Poisson process with parameter $\lambda>0$.
\begin{enumerate}
    \item Determine $\mathbb{E}\left[T_{12}\right]$ and $\operatorname{Var}\left(T_{12}\right)$.
    \item Determine $\mathbb{E}\left[T_{10} \mid\left\{N_2=5\right\} \cap\left\{T_3<2\right\}\right]$.
    \item Determine $\mathbb{E}\left[N_5 \mid N_2=7\right]$ and $\operatorname{Var}\left[N_5 \mid N_2=7\right]$. Also determine $\mathbb{E}\left[N_5 \mid N_2\right]$.
\end{enumerate}
\solution
\begin{enumerate}
    \item 
\end{enumerate}
\problem{3 - Durrett 2.27}
Rock concert tickets are sold at a ticket counter. Females and males arrive at times of independent Poisson processes with rates 30 and 20 customers per hour. 
\begin{enumerate}
    \item What is the probability the first three customers are female? 
    \item If exactly two customers arrived in the first five minutes, what is the probability both arrived in the first three minutes.
    \item Suppose that customers regardless of sex buy one ticket with probability $1 / 2$, two tickets with probability $2 / 5$, and three tickets with probability $1 / 10$. Let $N_i$ be the number of customers that buy $i$ tickets in the first hour. Find the joint distribution of $\left(N_1, N_2, N_3\right)$.
\end{enumerate}
\solution
\begin{enumerate}
    \item 
\end{enumerate}
\end{document}